---
params:
  project_id: "2026-05-MIC"
  folder: "projects/2026-05-MIC"
  applicant_id: 1901
  by_role: FALSE
  role: 
  anon: FALSE
output: rmdformats::robobook
---
<!-- THIS FILE IS NOT SUPPOSED TO BE KNITTED BY HAND
    INSTEAD IT IS KNIT AUTOMATICALLY 
    BY THE APPLICATIONS_REPORT.RMD FILE FOR EACH APPLICANT.
    YOU CAN EDIT THIS FILE IF YOU WANT TO CHANGE THE INFORMATION DISPLAYED FOR EACH APPLICANT
-->
```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(message = FALSE)
knitr::opts_chunk$set(warning = FALSE)

library(dplyr)
library(tidyr)
library(tibble)
library(ggplot2)
library(readr)
library(forcats)
library(correltools)
library(stringr)

# metadata: role profiles
role_profiles <- readr::read_csv(here::here(params$folder, "data/role_profiles_long.csv")) %>% 
  filter(project_id == params$project_id)

# contains all applications to all projects
gs_upload <- readr::read_csv(here::here(params$folder, "data/gs_upload.csv")) 
roles_df <- gs_upload %>% 
  filter(project_id == params$project_id) %>% 
  select(applicant_id, project_id, project_role)
  
# applicant data
wide <- readr::read_csv(here::here(params$folder, "data/wide.csv"))
a <- wide |> 
  filter(applicant_id == params$applicant_id) %>% 
  as.list()

# all applications of applicant
a$roles <- roles_df %>% 
  filter(applicant_id == params$applicant_id) %>% 
  select(-applicant_id)

# self assessment
ratings <- readr::read_csv(here::here(params$folder, "data/ratings.csv"))
a$ratings <- ratings %>% 
  filter(applicant_id == params$applicant_id) %>% 
  select(-applicant_id)
```


```{r fig.height=8, fig.width=6}
# theme and palette
theme_set(correltools::theme_correlaid(base_size = 12))
correlpal <- correltools::correlaid_pal()

# rating scale
rating_mapping <- tibble::tribble(~rating, ~rating_num, 
                                  "beginner", 1,
                                  "user", 2,
                                  "advanced", 3,
                                  "expert", 4)

```



```{r message=FALSE}
if (length(a) == 0) stop(glue::glue('There is no applicant with id {params$applicant_id}. Available ids: {paste(roles_df$applicant_id, collapse = ", ")}'))

gender_str <- stringr::str_replace(a$gender, '_', ' ')
role_str <- stringr::str_replace(a$roles$project_role %>% paste(collapse = ", "), '_', ' ')
```


```{r, results='asis'}
# header

if (params$by_role) {
  h <- sprintf("## %s - %s", a$applicant_id, gender_str)
  
} else {
  h <- sprintf("# %s - %s - %s", a$applicant_id, gender_str, role_str)
}
cat(h, sep = "\n")

```

**Gender**: `r gender_str`

**Project role(s) for this project**: `r role_str`

**All applications:**
```{r}
# count no of applications for all roles
roles_count <- roles_df %>% 
  count(project_id, project_role, name = "# applications for role")
a$roles %>% 
  left_join(roles_count, by = c("project_id", "project_role")) %>% 
  knitr::kable()
```

**German skills**: `r a$german_skills`

**D4GV Workshops**: `r a$d4gv_participation`

**Team coordinator tasks**: 
```{r results = 'asis'}
if ("team_coordinator" %in% a$roles$project_role) {
  cat("applied as team coordinator.")
} else {
  cat(a$team_coordinator_tasks)
}
```


**Past applications**

```{r results='asis'}
if (is.na(a$past_applications)) {
  cat('No information about past applications was collected')
}

if (a$past_applications == 'first_application') {
  cat('The applicant is applying to a CorrelAid project for the **first time**.')
} else if(a$past_applications == 'successful') {
    cat(glue::glue('The applicant has **successfully applied** to a CorrelAid project before.'))
} else if(a$past_applications == 'not_successful') {
    cat(glue::glue("The applicant was **not successful** with their application(s) so far. They specified the following when asked about when/where they have applied in the past:\n\n > {a$past_applications_details}"))
}
```

### Motivation & Skills

#### What skills qualify you?

`r a$motivation_skills`

#### Why do you want to get involved?

`r a$motivation_why`

#### What do you want to learn as a team trainee?

```{r results='asis'}
if ("team_trainee" %in% a$roles$project_role) {
  cat(a$motivation_tt)
} else {
  cat("does not apply")
}
```


#### Self-rated experience with tools, techniques and topics 

**optional answer to "other tools":**

```{r results='asis'}
a$ratings %>% filter(skill == "tools_other") %>% pull(rating) %>% cat()
```




```{css}
/* Make summary and arrow sit on the same line */
details summary {
  list-style: none;          /* remove default marker */
  cursor: pointer;
  display: flex;             /* key: keeps arrow + text aligned */
  align-items: center;       /* vertical alignment */
  gap: 0.4em;                /* space between arrow and text */
}

/* Hide default marker in WebKit browsers */
details summary::-webkit-details-marker {
  display: none;
}

/* Custom arrow */
details summary::before {
  content: "▸";
  transition: transform 0.2s ease;
  display: inline-block;
}

/* Rotate when open */
details[open] summary::before {
  transform: rotate(90deg);
}
```

```{r}
skill_plot <- function(ratings_role) {
  p <- ggplot(ratings_role, aes(y = fct_reorder(skill, -pos), color = question, group = question, x = rating_num)) +
    geom_segment(aes(
      y = fct_reorder(skill, -pos),
      yend = fct_reorder(skill, -pos),
      x = 1,
      xend = rating_num
    )) +
    geom_point(size = 3) +
    scale_color_correlaid_d()+
    theme(
      panel.grid.minor.y = element_blank(),
      panel.grid.major.y = element_blank(), 
      legend.position = "bottom"
    ) +
    scale_x_continuous(
      "level",
      limits = c(min(rating_mapping$rating_num), max(rating_mapping$rating_num)),
      breaks = seq(min(rating_mapping$rating_num), max(rating_mapping$rating_num), 1),
      labels = rating_mapping$rating
    ) +
    labs(y = NULL, color = "")
  return(p)
}
```


```{r results='asis', fig.height=8, fig.width=6}

if (params$by_role) {
  role_profile <- role_profiles %>% 
      filter(role == params$role)
  
  a_ratings_role <- a$ratings %>% 
    filter(skill %in% role_profile$skill) %>% 
    arrange(question, skill) %>% 
    mutate(pos = 1:n())
  
  cat(sprintf("**Skills for role %s**", params$role), sep = "\n")
  cat(sprintf("mean rating: %.2f", mean(a_ratings_role$rating_num, na.rm = TRUE)))
  
    p <- skill_plot(a_ratings_role)
    print(p)
} else {
  
  for (this_role in a$roles$project_role) {
    # filter role profile and then only show skills relevant to the role
    this_role_profile <- role_profiles %>% 
      filter(role == this_role)
    
    # filter ratings relevant to role
    a_ratings_role <- a$ratings %>% 
      filter(skill %in% this_role_profile$skill) %>% 
      arrange(question, skill) %>% 
      mutate(pos = 1:n())
    
    anchor_id <- sprintf("%s-%s", a$applicant_id, tolower(this_role))
    cat(sprintf("### Role %s - %.2f {#%s}\n\n", this_role,
              mean(a_ratings_role$rating_num, na.rm = TRUE), anchor_id))
    
    cat("<details>\n")
    cat(paste0("<summary><h4>Plot ", this_role, "</h4></summary>"))
    
    p <- skill_plot(a_ratings_role)
    print(p)
    
    cat("</details>\n")
  
    cat("\n")
  }
}
```


